CrypTool Script \\ Mathematics and Cryptography

### 2002-04-19 script-de/script-de.tex
This commit was manufactured by cvs2svn to create tag 'source-1-3-01x-beta-3'.

Hier werden die Daten mittels symmetrischer Verfahren
verschl"usselt: der Schl"ussel ist ein vom Absender zuf"allig
generierter Sitzungsschl"ussel (session key)\index{Session Key}, der nur f"ur diese
Nachricht verwendet wird. Anschlie"send wird dieser
Sitzungsschl"ussel mit Hilfe des asymmetrischen Verfahrens
verschl"usselt und zusammen mit der Nachricht an den Empf"anger
"ubertragen. Der Empf"anger kann den Sitzungsschl"ussel mit Hilfe
seines geheimen Schl"ussels bestimmen und mit diesem dann die
Nachricht entschl"usseln. Auf diese Weise nutzt man das bequeme
Schl"usselmanagement \index{Schl""usselmanagement} asymmetrischer
Verfahren und kann trotzdem gro"se Datenmengen schnell und effektiv mit
symmetrischen Verfahren verschl"usseln.

>>>>

Hier werden die Daten mittels symmetrischer Verfahren
verschl"usselt: der Schl"ussel ist ein vom Absender zuf"allig
generierter Sitzungsschl"ussel (session key), der nur f"ur diese
Nachricht verwendet wird. Anschlie"send wird dieser
Sitzungsschl"ussel mit Hilfe des asymmetrischen Verfahrens
verschl"usselt und zusammen mit der Nachricht an den Empf"anger
"ubertragen. Der Empf"anger kann den Sitzungsschl"ussel mit Hilfe
seines geheimen Schl"ussels bestimmen und mit diesem dann die
Nachricht entschl"usseln. Auf diese Weise nutzt man das bequeme
Schl"usselmanagement \index{Schl""usselmanagement} asymmetrischer
Verfahren und kann trotzdem gro"se Datenmengen schnell und effektiv mit
symmetrischen Verfahren verschl"usseln.

### 2002-04-19 script-gb/einfuerung_zahlentheorie-gb.tex
This commit was manufactured by cvs2svn to create tag 'source-1-3-01x-beta-3'.

\author{
(c) B. Esslinger, 1998-2002 \\
Frankfurt am Main \\
besslinger@web.de
}

@@

The {\em author} 
would like to take this opportunity to thank their colleagues in the company and
at the universities of Frankfurt, Giessen and Karlsruhe. They particularly thank
Dr. Peer Wichmann from the Karlsruhe computer science research centre
(Forschungszentrum Informatik, FZI) for his down-to-earth support.

\enlargethispage{0.5cm}
As at CrypTool, the quality of the script is enhanced through your suggestions
and ideas for improvement. I look forward to your feedback.

\vskip +7 pt \noindent
You will find the current version of CrypTool under \newline
  \href{http://www.CrypTool.de}{\tt http://www.CrypTool.de},~~
  \href{http://www.cryptool.com}{\tt http://www.CrypTool.com}~~ or~~
  \href{http://www.cryptool.org}{\tt http://www.CrypTool.org}.
%{
%\vskip + 7 pt \noindent
%The contact persons for this free tool are listed in the readme file for
%CrypTool.}
}

>>>>

\author{
(c) B. Esslinger, 1998-2002 \\
Frankfurt am Main
}

@@

The {\em author} Bernhard Esslinger 
would like to take this opportunity to thank their colleagues in the company and
at the universities of Frankfurt, Giessen and Karlsruhe. They particularly thank
Dr. Peer Wichmann from the Karlsruhe computer science research centre
(Forschungszentrum Informatik, FZI) for his down-to-earth support.

\enlargethispage{0.5cm}
As at CrypTool, the quality of the script is enhanced through your suggestions
and ideas for improvement. We look forward to your feedback.

\vskip +7 pt \noindent
You will find the current version of CrypTool under \newline
  \href{http://www.CrypTool.de}{\tt http://www.CrypTool.de},~~
  \href{http://www.cryptool.com}{\tt http://www.CrypTool.com}~~ or~~
  \href{http://www.cryptool.org}{\tt http://www.CrypTool.org}.
{
\vskip + 7 pt \noindent
The contact persons for this free tool are listed in the readme file for
CrypTool.}
}

### 2002-04-19 script-gb/script-gb.tex
This commit was manufactured by cvs2svn to create tag 'source-1-3-01x-beta-3'.

In this case the data is encrypted using symmetric procedures: the key is a
session key\index{Session key} generated by the sender randomly that is only used for this message.
This session key is then encrypted using the asymmetric procedure and
transmitted to the recipient together with the message. Recipients can determine
the session key using their secret keys and then use the session key to encrypt
the message. In this way, we can benefit from the easy key management \index{Key
management} of asymmetric procedures and encrypt large quantities of data
quickly and efficiently using symmetric procedures.

>>>>

In this case the data is encrypted using symmetric procedures: the key is a
session key generated by the sender randomly that is only used for this message.
This session key is then encrypted using the asymmetric procedure and
transmitted to the recipient together with the message. Recipients can determine
the session key using their secret keys and then use the session key to encrypt
the message. In this way, we can benefit from the easy key management \index{Key
management} of asymmetric procedures and encrypt large quantities of data
quickly and efficiently using symmetric procedures.
